---
title: "Feature engineering 1. Sentiment analysis of descriptions"
author: "Roberto Ruiz"
date: "9 de febrero de 2017"
output: html_document
---



<h4>In this notebook i will apply sentiment analysis classification to the description column. Finally I will check if there is some statistical difference if we use this new created variables. 

&nbsp;&nbsp;
<h4>We call the required libraries and the train data set:
&nbsp;&nbsp;

```{r}

packages <- c("jsonlite", "dplyr", "purrr")

purrr::walk(packages, library, character.only = TRUE, warn.conflicts = FALSE)


data <- fromJSON("../input/train.json")

vars <- setdiff(names(data), c("photos", "features"))
train_df <- map_at(data, vars, unlist) %>% tibble::as_tibble(.)

train_df$id<-seq(1:length(train_df$building_id)) #numerical ids!

```

&nbsp;&nbsp;
<h4>Secondly we apply sentiment analysis to the description column and we get a new data frame:
&nbsp;&nbsp;

```{r}

library(syuzhet)
library(DT)
sentiment <- get_nrc_sentiment(train_df$description)
datatable(head(sentiment))

```


<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

<div class="col2">
&nbsp;&nbsp;
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
data<-as.data.frame(colSums(sentiment))

data$sentiment<-rownames(data)

colnames(data)<-c("value", "sentiment")

library(Hmisc) #Capitalize first letter of sentiment names
data$Sentiment<-capitalize(data$sentiment)
data<-data[-11,]


library(ggplot2) #Pie of sentiments
library(scales)

#Create a theme
blank_theme <- theme_minimal()+
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    panel.grid=element_blank(),
    axis.ticks = element_blank(),
    plot.title=element_text(size=14, face="bold")
  )


#Pies:


bp<- ggplot(data[1:8,], aes(x="", y=value, fill=Sentiment)) +  
  blank_theme +geom_bar(width = 1, stat = "identity")+coord_polar("y", start=0)+scale_fill_brewer(palette="Dark2")+
  theme(axis.text.x=element_blank())

bp2<-ggplot(data[9:10,], aes(x="", y=value, fill=Sentiment)) +  
  blank_theme +geom_bar(width = 1, stat = "identity")+coord_polar("y", start=0)+scale_fill_brewer(palette="Dark2")+
  theme(axis.text.x=element_blank())

bp
bp2
```
</div>

&nbsp;

<h4>At this point we can check if the new variables can have some important influence in our machine learning model. For that we can run a couple of linear regressions and compare them:
&nbsp;

```{r, echo=FALSE}
train_df$interest<-ifelse(train_df$interest_level=="low",0, ifelse(train_df$interest_level=="medium",1,0))

```

```{r}
#mod 1 without sentiments

mod1<-lm(interest~bedrooms+price+bathrooms, data=train_df)
summary(mod1)

sentiment$id<-seq(1:nrow(sentiment))
sent_df<-merge(train_df,sentiment, by.x="id", by.y="id", all.x=T, all.y=T)

#mod2 with sentiments
mod2<-lm(interest~bedrooms+price+bathrooms+positive+negative, data=sent_df)
summary(mod2)
```
&nbsp;&nbsp;


<h4>As we can see, all the variables have a high significance level. Using only two of the new created variables (positive and negative) increment the r squared in some points. So, we can try to use sentiment classification in the construction of our machine learning model. 

If you find this noteboook interesting, give me an up!

&nbsp;&nbsp;